### 2018-11-14 Sections/cloud_quantum_computing.tex
Distributed grover

>>>>

% Distributed quantum search algorithm

\subsubsection{Distributed quantum search algorithm}\index{Distributed quantum search algorithm}

The Grover quantum search algorithm (Sec.~\ref{sec:quantum_search}) can be easily parallelised by partitioning the search space, and allocating a different partition to each node.

Suppose we wish to search over the $N$-bit space $x$, to find a satisfying solution to some oracle function \mbox{$f(x)=1$}. Let there be $M$ nodes available for computation, where for simplicity we assume $M$ is a power of 2. We designate each of the nodes a $\log_2 M$-bit identification number $y=(0,M-1)$. We now program each node to search over a smaller search space $x'$, which is \mbox{$N-\log_2 M$} bits in length. The input to each oracle is now,
\begin{align}
x = x'\frown y.
\end{align}
(`$\frown$' denotes string concatenation).

For example, with four nodes the 2-bit identification numbers are, 
\begin{align}
	y=\{00,01,10,11\}.
\end{align}
If the input search space is $N$-bits in length, then each of the nodes are assigned the search-space \mbox{$x'\frown y$}, where $x'$ is a \mbox{$N-2$}-bit number.

It can easily be seen that this approach is compatible with the quantum \textsc{MapReduce} formalism, where the \textsc{Map} function assigns the partitions denoted by $y$, and the \textsc{Reduce} function collects satisfying arguments. The net computational speedup is linear, simply a factor equal to the number of nodes, $M$. Note that this approach does not exploit entanglement between nodes, and does not offer a `quantum' (i.e super-linear) speedup, since it is really just brute-force partitioning of a problem into smaller more efficient ones that are attacked independently.

% Distributed unitary error averaging
